\papertitle

### 2014-03-19 final-report/paper.tex
Defined what a query fragment is. Small fixes to the abstract and intro..

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}

@@

We propose a visualization system for understanding and exploring query execution and data movement in a distributed database management system (DDBMS). Our tool provides insight into: (1) data flow between query fragments and between workers, (2) query execution and operator dependencies, (3) cluster utilization, (4) network utilization. Our tool, which we call \system, helps developers understand and improve query execution, and provides insight into common problems such as data skew or performance bottlenecks.

@@

Database query performance is often unpredictable, specially when the DBMS is distributed. This requires database 
administrators to spend significant amounts of time and effort isolating and debugging the root cause of performance 
problems. These may include skewed data partitioning or run-time issues, such as resource contention or 
adverse network conditions.

@@

\item An interactive visualization of the physical query plan. The physical query plan in Myria is composed of
a DAG of fragments, where each DAG link represents communication between workers, possibly over the network. 
\system displays this DAG in an interactive fashion with clickable elements for fragment nodes and communication links. 
This DAG also represents a high-level data flow in the DDBMS.

\item A view for cluster utilization and operator performance for each \emph{Myria} segment. Each segment is composed of
multiple sequential database operators running on the same worker. Upon clicking on a collapsed segment node in the
query plan DAG, the node expands to display the operators comprising the segment and renders the fragment execution view.
The fragment execution view visualizes the utilization of the cluster by showing whether each worker is busy working 
on the selected fragment. It also breaks down the work done by each worker into operators composing the fragment.

>>>>

\documentclass{chi2009}
\usepackage{times}
\usepackage{url}
\usepackage{graphics}
\usepackage{color}
\usepackage[pdftex]{hyperref}
\usepackage{xspace}
\usepackage{graphicx}

\usepackage{caption}
% Bug in my version of the caption package
\DeclareCaptionType{copyrightbox}
\usepackage{subcaption}
\usepackage{listings}

@@

We propose a visualization system to explore and understand query
execution and data movement in a distributed database management system
(DDBMS). Our tool provides insight into: (1) data flow between query segments
and between workers, (2) query execution and operator dependencies, (3) cluster
utilization, (4) network utilization. Our tool, \system, helps
developers understand and improve query execution, and provides insight into
common problems such as data skew or performance bottlenecks.

@@

Database query performance is often unpredictable, especially when the DBMS is
distributed. This requires programmers or database administrators to spend
significant amounts of time and effort isolating and debugging the root cause
of performance problems. These may include skewed data partitioning or run-time
issues, such as resource contention or adverse network conditions.

@@

\item An interactive visualization of the physical query plan. The physical
query plan is composed of a DAG of query \emph{fragments}. A query
fragment is a subtree of the query execution plan that is separated from the
rest of the plan by a network boundary. This means that the operators inside a
query fragment can be executed by a single thread. Each fragment is scheduled
to run on multiple workers, which means each worker thread executes the same set of
operators inside the fragment, but on different data. Each DAG link represents
communication between workers, possibly over the network.  \system displays
this DAG in an interactive fashion with clickable elements for fragment nodes
and communication links.  This DAG also represents a high-level data flow in
the DDBMS.

\item A view for cluster utilization and operator performance for each query fragment. Each fragment is composed of
multiple sequential database operators running on the same worker. Upon clicking on a collapsed fragment node in the
query plan DAG, the node expands to display the operators comprising the fragment and renders the fragment execution view.
The fragment execution view visualizes the utilization of the cluster by showing whether each worker is busy working 
on the selected fragment. It also breaks down the work done by each worker into operators composing the fragment.
